### 2012-05-22 docs/makefiles/makefiles.tex
finish for now

@@

@@

\subsection{Adding a Machine}

@@

>>>>

Several modules are included in all \maestro\ builds by default.
From \boxlib, we alway include:
\begin{itemize}
\item {\tt \$\{BOXLIB\_HOME\}/Src/F\_BaseLib}
\item {\tt \$\{BOXLIB\_HOME\}/Src/LinearSolvers/F\_MG}
\end{itemize}

\noindent From {\tt extern}, we always include
\begin{itemize}
\item {\tt extern/model\_parser}
\item {\tt extern/LAPACK}
\item {\tt extern/random}
\item {\tt extern/BLAS}
\item {\tt \$\{EOS\_DIR\}}
\item {\tt \$\{NETWORK\_DIR\}}
\item {\tt \$\{CONDUCTIVITY\_DIR\}}
\end{itemize}
for most networks, we automatically add in {\tt extern/VODE} as well.

\noindent From {\tt MAESTRO/}, we add
\begin{itemize}
\item {\tt MAESTRO/constants}
\item {\tt MAESTRO/Source}
\end{itemize}
(although see the unit tests section below regarding {\tt MAESTRO/Source}.

\noindent Finally, any extra directories listed in the {\tt EXTRA\_DIR}
variable are included.

For each of these included directories, {\tt GMaestro.mak} adds the list of source files
defined in their {\tt GPackage.mak} to the list of files to be compiled.
It also adds each of these directories to the {\tt vpath} as a directory
for the build process to search in for source files.

@@

Sometimes we only want to use a few of the standard \maestro\
routines, for example in a unit test where we are testing only a small
part of the \maestro\ algorithm indepenedently.  In this case, we
don't want to comple all of the files in {\tt MAESTRO/Source}.  If we
set {\tt UNIT\_TEST := t} in our problem's {\tt GNUmakefile}, then the
{\tt GPackage.mak} in {\tt MAESTRO/Source} is not read, so those files
are not automatically put into the list of files to compile.  Instead,
the problem should create its own {\tt GPackage.mak} listing only the
subset of files that are to be compiled.  {\tt MAESTRO/Source} is put
into the {\tt vpath} search path for sources, so those files will
still be found as needed.

@@

@@

Properties for different compilers are already defined in 
{\tt \$\{BOXLIB\_HOME\}/Tools/F\_mk/comps/}.
Each compiler is given its own file.  The appropriate file is included
into {\tt GMakedefs.mak} by looking at the {\tt COMP} variable and the
operating system.  These compiler files define the compiler flags for
both optimized and debug compiling.  Additionally, the variable {\tt
FCOMP\_VERSION} should be defined there, based on the output from the
compiler, to provide the compiler version for output into the {\tt
job\_info} file at runtime.
